### 2022-11-10 dissertation/chapters/08-results.tex
🚧 (results): WIP - Re-plotting case study

\begin{quote}
      \textit{
            ``Without data, you are just another person with an opinion.'' - W. Edwards Deming
      }
\end{quote}

The last step in the scientific process requires the presentation and objective discussion of empirical findings with good statistical backing. From the problem statements and motivations made in Chapter \ref{chap:introduction}, goals have been defined that broadly include literature studies and a sound empirical process. Thus far, the reader has been provided with a vast scope of background information relevant to the development of the \Acs{BHH}. Chapters \ref{chap:introduction} - \ref{chap:probability} provided the background information, literature studies and existing landscape of research for \acp{ANN}, \index{heuristic}heuristics/\index{optimiser}optimisers, \acp{HH} and probability theory. These elements all share common elements that are required to understand the proposed \Acp{BHH} which was presented in Chapter \ref{chap:bhh}. The details around the empirical process was formally proposed in the methodology as presented in Chapter \ref{chap:methodology}. Finally, the results for the empirical process can be presented and this chapter aims to provide these results.

As a reminder, the empirical process is split into two main experimental groups. These include a behavioural case study and set of comparative studies. This chapter is organised into the same logical pattern. Each of these experimental groups is provided as its own section for detailed analysis and discussion of findings. The remainder of the chapter is structured as follows:

\begin{itemize}
      \item \textbf{Section \ref{sec:results:overview}} provides a brief overview of the general empirical process, high level discussion points and a brief discussion on results interpretation.

      \item \textbf{Section \ref{sec:results:case_study}} provides a detailed analysis of the behaviour of the \Acs{BHH} over a few example runs during training and testing and is meant to introduce the analysis of the \Acs{BHH} from a behavioural characteristic point of view. In this section, focus is put on the learning process itself and to determine what happens during training. It aims to provide insight into ``how'' and ``when'' the \Acs{BHH} learning happens.

      \item \textbf{Section \ref{sec:results:standalone}} provides the first of a series of comparative studies. This section presents the comparative analysis that studies the performance capabilities of the baseline configuration of the \Acs{BHH} to that of standalone/individual low level \index{heuristic}heuristics/\index{optimiser}optimisers. The sections that follow focus on the effect of various parameters on the \Acs{BHH}.

      \item \textbf{Sections \ref{sec:results:heuristic_pool}} - \ref{sec:results:discounted_rewards} capture the results of these empirical processes and focus on the configuration of the \textit{heuristic pool}, the \textit{population size}, \textit{credit assignment strategies}, \textit{reselection} window size, \textit{replay} window size, \textit{reanalysis} window size, \textit{burn in}, \textit{normalisation} and \textit{discounted rewards}, respectfully.

      \item \textbf{Section \ref{sec:results:computational_requirements}} contains a brief discussion on the computational requirements.

      \item \textbf{Section \ref{sec:results:overfitting}} provides a brief discussion on overfitting.

      \item Finally, a summary of the findings is given in \textbf{Section \ref{sec:results:summary}}.
\end{itemize}

\section{Overview}
\label{sec:results:overview}

This section aims to provide a general high level discussion on the outcomes of the empirical process as an introduction to the more detailed discussions to follow. Consider again the goals that have been defined in \ref{chap:introduction}. The empirical component addresses three different angles of analysis:

\begin{enumerate}
      \item Analysing the behaviour of the \Acs{BHH} during training and testing to determine if the the concept works and that the \Acs{BHH} is indeed learning. This component looks at the \Acs{BHH} in isolation and simply evaluates the outcomes of its behaviour over a few example runs and repeats this process for two groups of \Acs{BHH} variants based on \textit{replay} window size.

      \item Comparing the performance capabilities of the \Acs{BHH} to that of well-known low-level \index{heuristic}heuristics that are well researched and understood. This component looks at how the \Acs{BHH} performs given a frame of reference to compare to. Careful consideration of results interpretation must be given here and is discussed in more detail below.

      \item Analysing the effects of various configurations of hyper-parameters for the \Acs{BHH}. This component looks at which parameters have a statistically significant impact on the outcomes of the \Acs{BHH}.
\end{enumerate}

It is important to briefly discuss how results should be interpreted. Traditionally, for typical low-level heuristic training, evaluation of performance is done at a chosen point in time and based on a particular dependent variable. This could be a fixed number of training steps/epochs, early stopped conditions or any other stopping condition. The metric of interest could be a loss value, an accuracy or a rank. Algorithms/heuristics in question are then logically ranked/organised according to their final solution and conclusions are made based on these findings. However, the following arguments suggest an alternative approach for this empirical study:

\begin{itemize}
      \item
            Since there does not exist any research on this specific implementation of \acp{HH} and its application to \acs{FFNN} training, there is no clear point at which it is known that the learning of the \acs{BHH} becomes detrimental to the training process. For example, there exists a currently unknown point during training where the performance bias towards the ``best'' \index{heuristic}heuristic no longer yield improved training or test generalisation outcomes. To cater for this, a fixed maximum number of training epochs have been chosen that empirically have been shown to be sufficient to notice diminishing returns in the outcome. \index{Early stopping}Early stopping was considered, but purposefully not implemented. This is to allow the study of the behaviour and capabilities of the \Acs{BHH} up to and beyond the point of diminishing returns.

      \item
            The training process is to some degree analogous and comparable to a dynamic optimisation problem as previously discussed. This means that the performance of \index{heuristic}heuristics, and thus the \Acs{BHH}, vary at different times during the training process. This hints to the hypothesis that was set in Chapter \ref{chap:introduction} and suggests that there is no single \index{heuristic}heuristic that is always the best \index{heuristic}heuristic to use during all of training. Rather, there exists an applicable, relevant \index{heuristic}heuristic (or combination of \index{heuristic}heuristics) to use at a given point in time during the training process and can change as the process continues. This means the selected \index{heuristic}heuristic at time step $t$ is not necessarily the best heuristic to select at timestamp $t+1$. This argument is further supported by the fact that these experiments are trained on mini-batches, resulting in a lot of noise during training. This noise can cause the \Ac{BHH} to want to "correct" a certain learnt belief. This introduces the same challenges as with \Ac{RL}: Consider delayed rewards, size of rewards, unlearning behaviour that is no longer required, all of which affect the training process throughout and not just at the point of stopping.
\end{itemize}

Based on the points made above, each experimental group is to be evaluated in isolation and has a specific area of focus. For all experimental groups, heuristics are evaluated during \textbf{all} the steps of the training and testing process. For this reason, ranking \index{heuristic}heuristic should not necessarily lead to the conclusion that one heuristic is \textit{better} than another, but rather, that there is a statistically significant difference between the outcomes of heuristics, relative to the entire training and testing process for a given experimental group. The authors suggest further research to include early stopping conditions for the ranking to make entirely sense. However, that does not mean the ranking approach is useless. It still provides a measure of comparison and is indeed indicative of statistically significant outcomes.

The points that have been discussed above have been observed during the empirical process. It is shown in the succeeding sections that the \Acs{BHH} is capable of training \Acp{FFNN} and that it does so relatively well. It is shown that the \Acs{BHH} is generally capable of providing good test generalisations when compared to existing low-level \index{heuristic}heuristics. However, it is shown that the majority of the influence of the \Acs{BHH} occurs during the first few epochs of the training process. Initially uniformly randomised candidate solutions has more room to learn in the initial phases of training in comparison to later phases where learning has become stagnated. It is also shown that this pivotal point of diminishing return is problem specific. Further to this pivotal point, it is shown that the \Acs{BHH} is subject to over-fitting, quite drastically. There are various conclusions that can be made from this point, but the detail is left to the relevant sections to follow.

The following section provides the results and findings for a behavioural case study of the \Acp{BHH} on the iris dataset.

\section{Case Study}
\label{sec:results:case_study}

This section provides a study on the behaviour of the \Acs{BHH} during training and testing. It is important to mention that this experimental group does not necessarily focus on the exact metrics, but rather on the general behaviour of the \Ac{BHH}. This means that statistical analysis and statistical certainty as is not required. Instead, a number of example runs have been executed purely for the intent of analysing behaviour. Furthermore, this behavioural case study is executed on a very small, but well-known toy dataset called \textit{iris}. Iris is not usually considered for full empirical processes due to its size and simplicity. Although there are fourteen other datasets to choose from, iris provides a very simple, relevant and relate-able case study that illustrate the necessary points sufficiently.

Figure \ref{fig:results:case_study:iris:metric_plots} illustrate these runs during training and testing. Take note of the legend as provided in Figure \ref{fig:results:case_study:iris:legend}. There are two variants of the \Acs{BHH} included here, each with three repeated runs, seeded according to run number:

\begin{itemize}
      \item \Acp{BHH} with a very \textbf{short memory}, i.e. replay windows size = 10
      \item \Acp{BHH} with a very \textbf{long memory}, i.e. replay windows size = 250
\end{itemize}

These two groups have been chosen as their parameters have been shown to provide drastically different outcomes from each other during training and forms a good basis for behavioural analysis. For more details on replay window size, see Section \ref{sec:results:replay}.

A breakdown of the run notation as provided in Figure \ref{fig:results:case_study:iris:legend} is then given as follows:

\begin{itemize}
      \item \textbf{iris} - The dataset in question
      \item \textbf{bhh} - The heuristic in question
      \item \textbf{hp:all} - The heuristic pool (hp) in question. ``All'' refers to all the implemented lower-level heuristics including both classical gradient-based heuristics/optimisers as well as meta-heuristics.
      \item \textbf{ps:5} - The population size (ps) in question. In this case, population size = 5.
      \item \textbf{bi:0} - The burn in window size (bi) in question. In this case, burn in window size = 0.
      \item \textbf{rp:10} - The replay window size (rp) in question. In this case, replay window size = 10.
      \item \textbf{rs:10} - The reselection window size (rp) in question. In this case, reselection window size = 10.
      \item \textbf{ra:10} - The reanalysis window size (rp) in question. In this case, reanalysis window size = 10.
      \item \textbf{nm:False} - The normalisation flag (nm) in question. In this case, normalisation is disabled.
      \item \textbf{ct:ibest} - The credit assignment strategy (ct) in question. In this case, the credit assignment strategy used is \textit{ibest}.
      \item \textbf{dr:False} - The discounted rewards flag (dr) in question. In this case, discounted rewards is disabled.
\end{itemize}

From figure \ref{fig:results:case_study:iris:metric_plots} it is shown that the \Acs{BHH} exhibit similar behaviours to that of lower-level heuristics. Figures \ref{fig:results:case_study:iris:train:loss} and \ref{fig:results:case_study:iris:train:accuracy} illustrates a smooth training process, converging to a well-known minimum loss for the iris dataset. In Figures \ref{fig:results:case_study:iris:test:loss} and \ref{fig:results:case_study:iris:test:accuracy} it is shown that the \Acs{BHH} generalised well on the test set. Generalisation improved up to about epoch 10 before overfitting starts occurring. From this, it can be concluded that most of the learning, for this particular dataset, takes place in the first 10 epochs of the training process. From this point onwards, the \Acs{BHH} tries to undo ``bad'' selections made earlier. It is interesting to notice that despite overfitting, the \Acs{BHH} was able to ``correct'' itself to some degree (up to epoch 20), but never really converged back on the minimum it reached up to epoch 10. Early stopping should prohibit this from happening, but this is left for further research.

\begin{figure}[htbp]
      \begin{subfigure}{0.49\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/train_loss.png}
            \caption{Train loss}
            \label{fig:results:case_study:iris:train:loss}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/test_loss.png}
            \caption{Test loss}
            \label{fig:results:case_study:iris:test:loss}
      \end{subfigure}
      \par\bigskip
      \begin{subfigure}{0.49\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/train_accuracy.png}
            \caption{Train accuracy}
            \label{fig:results:case_study:iris:train:accuracy}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/test_accuracy.png}
            \caption{Test accuracy}
            \label{fig:results:case_study:iris:test:accuracy}
      \end{subfigure}
      \par\bigskip
      \begin{subfigure}{\textwidth}
            \centering
            \includegraphics[width=0.35\textwidth]{bhh_case_study/iris/legend.png}
            \caption{Legend}
            \label{fig:results:case_study:iris:legend}
      \end{subfigure}
      \par\bigskip
      \caption{Train and test behaviour of the \Ac{BHH} baseline for different configurations of replay window size}
      \label{fig:results:case_study:iris:metric_plots}
\end{figure}

A high level view of the train and test metric plots is good for drawing high level conclusions, but more detail is required. Figure \ref{fig:results:case_study:iris:alpha} aims to provide more detail as to what is happening during training and plots the value of $\alpha$ during training. Each sub-figure represents the value of $\alpha$ for a particular index, representing a particular \index{heuristic}heuristic. From sub-figures \ref{fig:results:case_study:iris:alpha:0}, \ref{fig:results:case_study:iris:alpha:2} and \ref{fig:results:case_study:iris:alpha:6}, the effect of a larger replay value is clear. Although a more detailed discussed on replay window sizes is left for Section \ref{sec:results:replay}, one can clearly see the accumulation of ``knowledge''/``evidence'' in the concentration parameter $\alpha$. It should be noticeable then from these sub-figures how $\alpha$ changes over time for runs with lower replay window sizes and is indicative of the learning capabilities of the \Ac{BHH}.  From these changes, one can formulate a prediction of which \index{heuristic}heuristics are then likely to be selected in the next steps.

Figures \ref{fig:results:case_study:iris:alpha:5} and \ref{fig:results:case_study:iris:alpha:9} contain a run in orange that shows how the concentration for a particular heuristic (\Acs{Adadelta} and \Acs{DE}) and can change over time. This suggests that the \Acs{BHH} has the ability to dynamically switch between heuristics as the need requires. This concept bears similarities to dynamic optimisation algorithms. It can thus be said that an observation is made that the \Acs{BHH} is able to learn (to some degree) to balance exploration and exploitation by dynamically changing the heuristic of interest at that point in time. Notice that it has not yet been established if the attempt to balance leads to good or bad outcomes. However, this is a still a useful feature of the \Acs{BHH} and warrants further discussion and reasoning. These statements further support the hypothesis that there might not be a no single specific heuristic that is the best heuristic to train the \Acs{FFNN} during the entire training process. In the succeeding sections, it is shown how this statement is further supported as the behaviour of the \Acs{BHH} is shown to be problem-dependent.

A clear distinction between Figures \ref{fig:results:case_study:iris:metric_plots} and \ref{fig:results:case_study:iris:alpha} should be pointed out. Figures \ref{fig:results:case_study:iris:metric_plots} plot metrics for every epoch, while Figure \ref{fig:results:case_study:iris:alpha} plot metrics for every mini-batch iteration. This is a subtle difference in visualisation, but nonetheless important. A more fine-grained visualisation illustrates the learning opportunities better since it is clear that a single step of learning happens on a single mini-batch iteration. This is important to keep in mind for various different sizes of datasets.

\begin{figure}[htbp]
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[0].png}
            \caption{$\alpha_{0}$ - \Acs{SGD}}
            \label{fig:results:case_study:iris:alpha:0}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[1].png}
            \caption{$\alpha_{1}$ - \Acs{Momentum}}
            \label{fig:results:case_study:iris:alpha:1}
      \end{subfigure}
      \par\bigskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[2].png}
            \caption{$\alpha_{2}$ - \Acs{NAG}}
            \label{fig:results:case_study:iris:alpha:2}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[3].png}
            \caption{$\alpha_{3}$ - \Acs{Adagrad}}
            \label{fig:results:case_study:iris:alpha:3}
      \end{subfigure}
      \par\bigskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[4].png}
            \caption{$\alpha_{4}$ - \Acs{RMSProp}}
            \label{fig:results:case_study:iris:alpha:4}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[5].png}
            \caption{$\alpha_{5}$ - \Acs{Adadelta}}
            \label{fig:results:case_study:iris:alpha:5}
      \end{subfigure}
      \par\bigskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[6].png}
            \caption{$\alpha_{6}$ - \Acs{Adam}}
            \label{fig:results:case_study:iris:alpha:6}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[7].png}
            \caption{$\alpha_{7}$ - \Acs{PSO}}
            \label{fig:results:case_study:iris:alpha:7}
      \end{subfigure}
      \par\bigskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[8].png}
            \caption{$\alpha_{8}$ - \Acs{GA}}
            \label{fig:results:case_study:iris:alpha:8}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[9].png}
            \caption{$\alpha_{9}$ - \Acs{DE}}
            \label{fig:results:case_study:iris:alpha:9}
      \end{subfigure}
      \par\bigskip
      \caption{Change in the concentration of $\alpha$ during training for various heuristics}
      \label{fig:results:case_study:iris:alpha}
\end{figure}

Due to the Bayesian nature of the \Acs{BHH}, one can expect the plots from figure \ref{fig:results:case_study:iris:alpha} to drive the plots presented in \ref{fig:results:case_study:iris:p_theta} as these two parameters are related. The parameter $\alpha$ is the concentration parameter for the Dirichlet probability distribution represented by $\theta$. The reader is now urged to consider Figures \ref{fig:results:case_study:iris:alpha:6} and \ref{fig:results:case_study:iris:p_theta:6} together. These two figures illustrate the above mentioned Bayesian concepts well. It should be noted that as $\alpha$ changes, $\theta$ will change. More specifically, the longer the ``memory'' of the \Acs{BHH} the greater the magnitude of $\alpha$ resulting in a sampled selection probability $\theta$ that converges to the ``learnt'' expected selection probability ($E\left[\theta\right]$). The impact of this concept (retained memory) is addressed in Sections \ref{sec:results:replay}.

\begin{figure}[htbp]
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/theta[0].png}
            \caption{$P(\theta_{0} | \alpha)$ - \Acs{SGD}}
            \label{fig:results:case_study:iris:p_theta:0}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/theta[1].png}
            \caption{$P(\theta_{1} | \alpha)$ - \Acs{Momentum}}
            \label{fig:results:case_study:iris:p_theta:1}
      \end{subfigure}
      \par\medskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/theta[2].png}
            \caption{$P(\theta_{2} | \alpha)$ - \Acs{NAG}}
            \label{fig:results:case_study:iris:p_theta:2}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/theta[3].png}
            \caption{$P(\theta_{3} | \alpha)$ - \Acs{Adagrad}}
            \label{fig:results:case_study:iris:p_theta:3}
      \end{subfigure}
      \par\medskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/theta[4].png}
            \caption{$P(\theta_{4} | \alpha)$ - \Acs{RMSProp}}
            \label{fig:results:case_study:iris:p_theta:4}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/theta[5].png}
            \caption{$P(\theta_{5} | \alpha)$ - \Acs{Adadelta}}
            \label{fig:results:case_study:iris:p_theta:5}
      \end{subfigure}
      \par\medskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/theta[6].png}
            \caption{$P(\theta_{6} | \alpha)$ - \Acs{Adam}}
            \label{fig:results:case_study:iris:p_theta:6}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/theta[7].png}
            \caption{$P(\theta_{7} | \alpha)$ - \Acs{PSO}}
            \label{fig:results:case_study:iris:p_theta:7}
      \end{subfigure}
      \par\medskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/theta[8].png}
            \caption{$P(\theta_{8} | \alpha)$ - \Acs{GA}}
            \label{fig:results:case_study:iris:p_theta:8}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/theta[9].png}
            \caption{$P(\theta_{9} | \alpha)$ - \Acs{DE}}
            \label{fig:results:case_study:iris:p_theta:9}
      \end{subfigure}
      \par\medskip
      \caption{Change in the sampled selection probability of $\theta$ during training for various heuristics}
      \label{fig:results:case_study:iris:p_theta}
\end{figure}

Another observation that can be made from Figures \ref{fig:results:case_study:iris:alpha} and \ref{fig:results:case_study:iris:p_theta} is that none of the runs are the same. This is of course due to the stochastic nature of the \Acs{BHH} and the noise caused by using mini-batches. However, it highlights the fact that the learning process for the \Acs{BHH} has to be adaptive from run to run. This is evident in the plots presented in Figure \ref{fig:results:case_study:iris:p_H} as one can see how the \index{heuristic}heuristic selection probability changes over time. This is proof that the \Ac{BHH} is learning something, but it is yet to be established what exactly it is learning. It is said that the \Acs{BHH} updates its \textit{beliefs} (prior knowledge) about which heuristic to select by biasing selection towards \index{heuristic}heuristic performance. It can therefore be concluded that any learning that is done, is done as a result of learning from performance. Since the performance criteria mechanism for the \Ac{BHH}, called the \textit{credit assignment strategy} marks a successful event as one meeting the performance criteria. Although this event is very much a local event, the continuous application of it over all runs means that learning does account for positive learning towards the overall performance goals.

\begin{figure}[htbp]
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[0].png}
            \caption{$P\left(h_{0} | \theta \right)$ - \Acs{SGD}}
            \label{fig:results:case_study:iris:p_H:0}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[1].png}
            \caption{$P\left(h_{1} | \theta \right)$ - \Acs{Momentum}}
            \label{fig:results:case_study:iris:p_H:1}
      \end{subfigure}
      \par\medskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[2].png}
            \caption{$P\left(h_{2} | \theta \right)$ - \Acs{NAG}}
            \label{fig:results:case_study:iris:p_H:2}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[3].png}
            \caption{$P\left(h_{3} | \theta \right)$ - \Acs{Adagrad}}
            \label{fig:results:case_study:iris:p_H:3}
      \end{subfigure}
      \par\medskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[4].png}
            \caption{$P\left(h_{4} | \theta \right)$ - \Acs{RMSProp}}
            \label{fig:results:case_study:iris:p_H:4}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[5].png}
            \caption{$P\left(h_{5} | \theta \right)$ - \Acs{Adadelta}}
            \label{fig:results:case_study:iris:p_H:5}
      \end{subfigure}
      \par\medskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[6].png}
            \caption{$P\left(h_{6} | \theta \right)$ - \Acs{Adam}}
            \label{fig:results:case_study:iris:p_H:6}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[7].png}
            \caption{$P\left(h_{7} | \theta \right)$ - \Acs{PSO}}
            \label{fig:results:case_study:iris:p_H:7}
      \end{subfigure}
      \par\medskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[8].png}
            \caption{$P\left(h_{8} | \theta \right)$ - \Acs{GA}}
            \label{fig:results:case_study:iris:p_H:8}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[9].png}
            \caption{$P\left(h_{9} | \theta \right)$ - \Acs{DE}}
            \label{fig:results:case_study:iris:p_H:9}
      \end{subfigure}
      \par\medskip
      \caption{Change in the prior heuristic selection probability $P\left(H\right | \theta )$ as the \Ac{BHH} learns during training}
      \label{fig:results:case_study:iris:p_H}
\end{figure}

Consider now Figure \ref{fig:results:case_study:iris:p_theta:6} again, but this time include a configuration of the \Acs{BHH} where no \index{Bayesian Analysis}Bayesian Analysis takes place, resulting in a purely random \index{heuristic}heuristic selection probability throughout. Such an configuration is given in Figure \ref{fig:results:case_study:iris:no_learn:metrics} below for the sampled \index{heuristic}heuristic selection probability for \Acs{Adam} (gray).

\begin{figure}[htbp]
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/no_learning_theta.png}
            \caption{$P(\theta_{6} | \alpha)$}
            \label{fig:results:case_study:iris:no_learn:p_theta}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/no_learning_test_loss.png}
            \caption{Test loss}
            \label{fig:results:case_study:iris:no_learn:test:loss}
      \end{subfigure}
      \par\bigskip
      \caption{Comparing baseline \Acp{BHH} to that of a \Ac{BHH} with pure random selection.}
      \label{fig:results:case_study:iris:no_learn:metrics}
\end{figure}

One can see that the random configuration (gray) illustrated almost a fixed pattern behaviour, from which we can draw the following conclusions:

\begin{itemize}
      \item Despite a completely random heuristic selection probability, the underlying \Acs{BHH} was still able to learn and perform relatively well. If the ability to learn is then purely based on the \textit{perturbative} components of the \Acs{BHH} it can be concluded that the proxied heuristic step operations are successful.

      \item This shows that the \Acs{BHH} selection mechanism is indeed facilitating a learning process and since \Acs{Adam} is known to perform well on the iris dataset, it can be concluded that the learning process is successful and beneficial to the outcome of the \Acs{BHH}.
\end{itemize}

The statements made above conclude the successful working of the \Acs{BHH}. Both the perturbative element (through proxied heuristic update steps) and the selection mechanism (through Bayesian analysis) is shown to work successfully. Figure \ref{fig:results:case_study:iris:p_HgEC} shows the resulting output of the predictive model for each of the five entities in the heuristic pool. This predicted heuristic selection probability is used to parameterise a new categorical distribution from which the heuristics are finally sampled and (re)selected.

\begin{figure}[htbp]
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/p_HgEC[0][6].png}
            \caption{$P\left(h_{6}|e_{0},c_{1}\right)$ - entity 0 + \Acs{Adam} }
            \label{fig:results:case_study:iris:p_HgEC:0:6}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/p_HgEC[1][6].png}
            \caption{$P\left(h_{6}|e_{1},c_{1}\right)$ - entity 1 + \Acs{Adam} }
            \label{fig:results:case_study:iris:p_HgEC:1:6}
      \end{subfigure}
      \par\bigskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/p_HgEC[2][6].png}
            \caption{$P\left(h_{6}|e_{2},c_{1}\right)$ - entity 2 + \Acs{Adam} }
            \label{fig:results:case_study:iris:p_HgEC:2:6}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_case_study/iris/p_HgEC[3][6].png}
            \caption{$P\left(h_{6}|e_{3},c_{1}\right)$ - entity 3 + \Acs{Adam} }
            \label{fig:results:case_study:iris:p_HgEC:3:6}
      \end{subfigure}
      \par\bigskip
      \begin{subfigure}{\textwidth}
            \centering
            \includegraphics[width=0.5\textwidth]{bhh_case_study/iris/p_HgEC[4][6].png}
            \caption{$P\left(h_{6}|e_{4},c_{1}\right)$ - entity 4 + \Acs{Adam} }
            \label{fig:results:case_study:iris:p_HgEC:4:6}
      \end{subfigure}
      \par\bigskip
      \caption{Change in the realised output of the predictive model $P\left(H|E,C;\theta,\phi,\psi \right)$ showcasing the selection of the \Acs{Adam} optimiser/low-level heuristic as an example}
      \label{fig:results:case_study:iris:p_HgEC}
\end{figure}

Figure \ref{fig:results:case_study:iris:HgEC} show the resulting selected \index{heuristic}heuristic, per entity, over time. From these plots, one can see how convergence on \Acs{Adam} occurs at least at some point during training for the majority of the entities.

>>>>

\begin{quotation}
      \noindent ``Without data, you are just another person with an opinion.''
\end{quotation}
\begin{flushright}
      - W. Edwards Deming
\end{flushright}

\noindent
All the required background information on all the elements relevant to the empirical process have been presented in Chapters~\ref{chap:anns}-\ref{chap:probability}. The proposed \acf{BHH} was presented in Chapter~\ref{chap:bhh} and the design and methodology of the empirical process was presented in Chapter~\ref{chap:methodology}. The methodology presented a number of experiments to conduct, including a case study on the behaviour of the \acs{BHH} during training, and a comparison to the performance of state-of-the-art, standalone, low-level heuristics. The methodology also defined a number of experiments related to the empirical testing of the effects of hyper-parameters on the outcomes of the \acs{BHH}.

Finally, this chapter provides the outcome of these empirical processes and provides results on all the experiments that have been conducted. Detailed discussions follow on the outcomes of each experiment. Discussions are accompanied by figures and plots to help provide visual aid for the discussions. All experiments and discussions also provide the outcome of the statistical analysis of the results. The remainder of the chapter is structured as follows.

\begin{itemize}
      \item \textbf{Section \ref{sec:results:case_study}} provides detailed discussions on the outcomes of the case study on the behaviour of the \acs{BHH}. Illustrations are provided to show the outcomes of the learning process of the \acs{BHH}, while training the underlying \acf{FFNN}.

      \item \textbf{Section \ref{sec:results:bhh_vs_low_level_heuristics}} provides the results of the performance of the \acs{BHH} compared to individual low-level heuristics as it relates to all datasets. Three variants of the \acs{BHH} are included in these results. These include the baseline configuration, as well as a configuration that only includes gradient-based heuristics in the \index{heuristic pool}heuristic pool, and a configuration that only includes meta-heuristics in the \index{heuristic pool}heuristic pool.

      \item \textbf{Section \ref{sec:results:bhh_variant_hp}} provides the results for the experimental group that analyses the effects of the \index{heuristic pool}\textit{heuristic pool} hyper-parameter on the outcomes of the \acs{BHH}.

      \item \textbf{Section \ref{sec:results:bhh_variant_population}} provides the results for the experimental group that analyses the effects of the \textit{population size} hyper-parameter on the outcomes of the \acs{BHH}.

      \item \textbf{Section \ref{sec:results:bhh_variant_burn_in}} provides the results for the experimental group that analyses the effects of the \textit{burn in window size} hyper-parameter on the outcomes of the \acs{BHH}.

      \item \textbf{Section \ref{sec:results:bhh_variant_credit}} provides the results for the experimental group that analyses the effects of the \textit{credit assignment strategy} hyper-parameter on the outcomes of the \acs{BHH}.

      \item \textbf{Section \ref{sec:results:bhh_variant_replay}} provides the results for the experimental group that analyses the effects of the \textit{replay window size} hyper-parameter on the outcomes of the \acs{BHH}.

      \item \textbf{Section \ref{sec:results:bhh_variant_reanalysis}} provides the results for the experimental group that analyses the effects of the \textit{reanalysis interval} hyper-parameter on the outcomes of the \acs{BHH}.

      \item \textbf{Section \ref{sec:results:bhh_variant_reselection}} provides the results for the experimental group that analyses the effects of the \textit{reselection interval} hyper-parameter on the outcomes of the \acs{BHH}.

      \item \textbf{Section \ref{sec:results:bhh_variant_normalise}} provides the results for the experimental group that analyses the effects of the \textit{normalisation} hyper-parameter on the outcomes of the \acs{BHH}.

      \item \textbf{Section \ref{sec:results:bhh_variant_discounted_rewards}} provides the results for the experimental group that analyses the effects of the \textit{discounted rewards} hyper-parameter on the outcomes of the \acs{BHH}.

      \item \textbf{Section \ref{sec:results:overfitting}} provides a brief discussion on overfitting as it is observed for some of the empirical tests.

      \item \textbf{Section \ref{sec:results:computational_req}} provides a brief discussion on the practical application of the \acs{BHH} to real-world problems.

      \item \textbf{Section \ref{sec:results:overview}} provides an overview of all the results for all the empirical tests, followed by a brief discussion on the overall performance of the \acs{BHH}.

      \item \textbf{Section \ref{sec:results:overview}} provides a brief summary of the chapter.
\end{itemize}
